Forecasting Multi-District Elections

### 2019-11-23 outputs/paper/paper.Rmd
Update with updated SmartVote data

summary_stats %>%
  kable(format = "latex", 
        booktabs = TRUE, 
        digits = 2, 
        format.args = list(big.mark = ","),
        caption = "First preferences from the Smartvote Australia and Life in Australia datasets, by state",
        linesep = ""
        )  
# %>% 
#   kable_styling(font_size = 8)

@@

LINA_summary_education <- read_csv(here::here("outputs/data/tables/education_surveyed.csv")) %>% 
  rename(Class = Education) %>% 
  mutate(Type = c("Education", "", "", "", "")) %>% 
  select(Type, Class, Number, Proportion)

@@

SmartVote_summary_education <- tibble(Type = c("Education", "", "", "", ""),
                                      Class = c("High school", "Grad. dip.", "Bachelor", "Postgraduate", "Unknown"),
                                      Number = c("-", "-", "-", "-", "-"),
                                      Proportion = c("-", "-", "-", "-", "-"))

@@

both %>%
  kable(format = "latex", 
        booktabs = TRUE,
        digits = 2, 
        format.args = list(big.mark = ","),
        caption = "Descriptive statistics of the datasets.",
        linesep = ""
        )%>% 
  kableExtra::add_header_above(c(" " = 2, "Life in Australia" = 2, "Smartvote" = 2))

@@

After cleaning and adjustment we have 58,972 responses.

>>>>

summary_stats %>%
  kable(format = "latex", 
        booktabs = TRUE, 
        digits = 2, 
        format.args = list(big.mark = ","),
        caption = "First preferences from the survey datasets, by state",
        linesep = ""
        )  
# %>% 
#   kable_styling(font_size = 8)

@@

LINA_summary_education <- read_csv(here::here("outputs/data/tables/education_surveyed.csv")) %>% 
  rename(Class = Education) %>% 
  filter(Class != "Unknown") %>% 
  mutate(Type = c("Education", "", "", "")) %>% 
  select(Type, Class, Number, Proportion)

@@

SmartVote_summary_education <- read_csv(here::here("outputs/data/tables/SmartVote-education_surveyed.csv")) %>% 
  rename(Class = Education) %>% 
  mutate(arranger = c(3, 4, 2, 1)) %>% 
  arrange(arranger) %>% 
  mutate(Type = c("Education", "", "", "")) %>% 
  select(Type, Class, Number, Proportion)

SmartVote_summary_education$Class[SmartVote_summary_education$Class == "highSchoolorCertIorIIorLess"] <- "High school"
SmartVote_summary_education$Class[SmartVote_summary_education$Class == "gradDipDipCertIIIandIV"] <- "Grad. dip."
SmartVote_summary_education$Class[SmartVote_summary_education$Class == "bachelorDegree"] <- "Bachelor"
SmartVote_summary_education$Class[SmartVote_summary_education$Class == "postgraduateDegree"] <- "Postgraduate"

@@

both %>%
  kable(format = "latex", 
        booktabs = TRUE,
        digits = 2, 
        format.args = list(big.mark = ","),
        caption = "Descriptive statistics of the datasets",
        linesep = ""
        )%>% 
  kableExtra::add_header_above(c(" " = 2, "Life in Australia" = 2, "Smartvote" = 2))

@@

After cleaning and adjustment we have 53,310 responses.
